Supplementary Report for the article *Functional diversity can facilitate the collapse of an undesirable ecosystem state*

### 2022-10-23 reports/old/checks_puzzles/checks_puzzles.Rmd
large revision
Completely restructured and updated to microxanox version 0.9.1

## Setup parameter

```{r}
options(mc.cores = 7)

@@

parameter <- new_ss_by_a_N_parameter(
  dynamic_model = parameter$dynamic_model,
  event_definition = parameter$event_definition,
  event_interval = 100000,
  noise_sigma = parameter$noise_sigma,
  minimum_abundances = minimum_abundances,
  sim_duration = 100000,  ##    Was 1e6
  sim_sample_interval = 100000,
  log10a_series = parameter$log10a_series,
  solver_method = parameter$solver_method,
  ss_expt = ss_expt
)
rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)

@@

### Run stable state finding

@@

```{r run_experiment, eval = eval_dynamics_flag}
run_ss_var_experiment(
  parameter = readRDS(here("experiments/checks_puzzles/data/parameter_1e5_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/checks_puzzles/data/var_expt_1e5_x2x6_factorial.RDS"))) %>%
saveRDS(here("experiments/checks_puzzles/data/ss_data_1e6_x2x5_factorial.RDS"))
```

### Process the stable state data

@@

```{r, eval = FALSE, echo = FALSE}
var_expt1 <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
var_expt2 <- readRDS(here("experiments/checks_puzzles/data/ss_data_1e5_x2x6_factorial.RDS"))

p1_short  <- plot_ss_result1(var_expt2,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1_short

p1_long  <- plot_ss_result1(var_expt1,
                result_index = max_diversty_all,
                filename_prefix = NULL,
                save_image_file = FALSE)
p1_long
```

# Puzzle 1

@@

```{r, eval = FALSE, echo = FALSE}
sim_res_novar1 <- readRDS(here("experiments/checks_puzzles/data/puzzle1_1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

```{r eval = FALSE, echo = FALSE}
parameter$strain_parameter <- var_expt[max_only_SBPB_diversity,]$pars[[1]]
#parameter$sim_duration <- 100000
#parameter$result <- NULL
#parameter$log10a_series <- c(-5.2, -5.2)
#parameter$strain_parameter$initial_state <- new_initial_state(
#  nrow(parameter$strain_parameter$CB),
#  nrow(parameter$strain_parameter$PB),
#  nrow(parameter$strain_parameter$PB),
#  values = "bush_ssfig3"
#)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/checks_puzzles/data/puzzle1_2.RDS"))
```

```{r, eval = FALSE, echo = FALSE}
sim_res_highvar1 <- readRDS(here("experiments/checks_puzzles/data/puzzle1_2.RDS"))
plot_dynamics(sim_res_highvar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

## Zoom in on SS

@@

## Negative abundance investigation

@@

## Understand about relative and absolute variation in traits

>>>>

## Setup and processing

Run a shorter sim:

```{r eval = eval_dynamics_flag}

sim_length <- 100000

options(mc.cores = 7)

@@

parameter <- new_ss_by_a_N_parameter(
  dynamic_model = parameter$dynamic_model,
  event_definition = parameter$event_definition,
  event_interval = sim_length,
  noise_sigma = parameter$noise_sigma,
  minimum_abundances = minimum_abundances,
  sim_duration = sim_length,  ##    Was 1e6
  sim_sample_interval = sim_length,
  log10a_series = parameter$log10a_series,
  solver_method = parameter$solver_method,
  ss_expt = ss_expt
)
rm(minimum_abundances, grid_num_a, a_Os, grid_num_N, initial_CBs, initial_PBs, initial_SBs, ss_expt)

@@

@@

```{r run_experiment, eval = eval_dynamics_flag}
run_ss_var_experiment(
  parameter = readRDS(here("experiments/checks_puzzles/data/parameter_1e5_x2x6_factorial.RDS")), 
  var_expt = readRDS(here("experiments/checks_puzzles/data/var_expt_1e5_x2x6_factorial.RDS"))) %>%
  saveRDS(here("experiments/checks_puzzles/data/ss_data_1e5_x2x6_factorial.RDS"))
```

@@

## Visualise

```{r}
var_expt1 <- readRDS(here("experiments/9_strains/data/ss_data_1e6_x2x6_factorial.RDS"))
var_expt2 <- readRDS(here("experiments/checks_puzzles/data/ss_data_1e5_x2x6_factorial.RDS"))

p1_short  <- plot_ss_result1(var_expt2,
                result_index = nrow(var_expt2),
                filename_prefix = NULL,
                save_image_file = FALSE)
p1_short

p1_long  <- plot_ss_result1(var_expt1,
                result_index = nrow(var_expt1),
                filename_prefix = NULL,
                save_image_file = FALSE)
p1_long
```

## Continute here to check the stability measures.

# Hidden effect of sulphur bacteria diversity

@@

```{r}
sim_res_novar1 <- readRDS(here("experiments/checks_puzzles/data/puzzle1_1.RDS"))
plot_dynamics(sim_res_novar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

```{r eval = eval_dynamics_flag}
parameter$strain_parameter <- var_expt[max_only_SBPB_diversity,]$pars[[1]]
#parameter$sim_duration <- 100000
#parameter$result <- NULL
#parameter$log10a_series <- c(-5.2, -5.2)
#parameter$strain_parameter$initial_state <- new_initial_state(
#  nrow(parameter$strain_parameter$CB),
#  nrow(parameter$strain_parameter$PB),
#  nrow(parameter$strain_parameter$PB),
#  values = "bush_ssfig3"
#)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1, here("experiments/checks_puzzles/data/puzzle1_2.RDS"))
```

```{r}
sim_res_highvar1 <- readRDS(here("experiments/checks_puzzles/data/puzzle1_2.RDS"))
plot_dynamics(sim_res_highvar1)
#ggsave(here("simulations/expt2/figures/switching_novar.pdf"), width = 10)
```

# Zoom in on SS

@@

# Negative abundance investigation

@@

# Understand about relative and absolute variation in traits

### 2022-10-23 reports/supplement/supplement_0.9.1.Rmd
large revision
Completely restructured and updated to microxanox version 0.9.1

```{r echo = FALSE}
rm(list = ls())
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("r", "various_useful_functions.r"))
# source(here("experiments", "1_figures_main_ms", "ms_figure_functions.r"))
source(here("experiments", "1_figures_main_ms", "figures_main_ms_v1.R"))

@@

@@

```{r repl-meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
temp_meth <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
```

@@

```{r both-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:both-meth1)', fig.height=8, fig.width=8, fig.align="center"}
repl_method_1 <- repl_meth$ss_res[[1]] %>%
     mutate(time = NA,
            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  select(names(temp_meth$ssfind_result[[1]]))

@@

```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data", "0_ss_finding", "replication_method", "processed_data", "stab_data_replication_method.RDS"))

sim_length <- 1e6
num_strains <- 9
plot_here <- all_stab %>%
  filter(simlength == sim_length)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

```{r repl-meth-ex1, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth-ex1)', fig.height=10, fig.width=8, fig.align="center"}
repl_meth <- readRDS(here("data", "0_ss_finding", "replication_method", "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
fig_state_vs_o2diff_sidebyside_alternative(repl_meth[94,])
```

@@

```{r div-temp-eventdef1, eval = TRUE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "event_def1", "processed_data", "stab_data_temporal_method.RDS"))

wait_time <- 1e6
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS"))

@@

```{r ss-temp-meth3, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=10, fig.width=8, fig.align="center"}
single_1e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_1e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
```

@@

```{r ss-temp-meth4, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=10, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("data", "0_ss_finding", "temporal_method", "single_2e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
```

@@

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=10, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))

@@

fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[13,])

@@

```{r ss-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth2)', fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[14,])
```

@@

```{r eval = run_sims_this_section, echo = FALSE}
#var_expt <- readRDS(here::here("data", "9_strains", "ss_data_1e6_x2x6_factorial.RDS"))
var_expt_levels <- var_expt[,1:6]
no_diversity <- which(rowSums(abs(var_expt_levels))==0)
max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
                            rowSums(abs(var_expt_levels)))
max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
                            rowSums(abs(var_expt_levels[,1:2])) &
                              rowSums(abs(var_expt_levels[,3:6]))==0)
max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)
```

@@

sim_res_novar1 <- run_simulation(parameter)
dir.create(here::here("data", "2_supplement"), recursive = TRUE, showWarnings = FALSE)
saveRDS(sim_res_novar1, here::here("data", "2_supplement", "puzzle1_1.RDS"))
```

@@

```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_novar1 <- readRDS(here::here("data", "2_supplement", "puzzle1_1.RDS"))
p <- plot_dynamics(sim_res_novar1)
p[[1]] <- p[[1]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[2]] <- p[[2]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[3]] <- p[[3]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[4]]$data <- p[[4]]$data %>% 
  dplyr::filter(species != "a")
p[[4]]$data$species <- p[[4]]$data$species %>%
  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
p[[4]] <- p[[4]] + 
  xlab("time (h)") + 
  ylab(expression(log[10](concentration)~(µM))) + 
  labs(colour = "substrate") +
  theme_bw()

@@

```{r  eval = run_sims_this_section, echo = FALSE}
parameter$strain_parameter <- var_expt[max_only_SBPB_diversity,]$pars[[1]]
#parameter$sim_duration <- 100000
#parameter$result <- NULL
#parameter$log10a_series <- c(-5.2, -5.2)
#parameter$strain_parameter$initial_state <- new_initial_state(
#  nrow(parameter$strain_parameter$CB),
#  nrow(parameter$strain_parameter$PB),
#  nrow(parameter$strain_parameter$PB),
#  values = "bush_ssfig3"
#)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1,here::here("data", "2_supplement", "puzzle1_2.RDS"))
```

@@

```{r sb-div-effect4, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect4)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_highvar1 <- readRDS(here("data", "2_supplement", "puzzle1_2.RDS"))

@@

```{r echo = FALSE}
ss_9s <- readRDS(here::here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
only_PB_variable <- ss_9s %>%
  filter(
    abs(CB_var_gmax_s) < 0.0001,
    abs(SB_var_gmax_s) < 0.0001
  )
only_PB_variable <- only_PB_variable[order(only_PB_variable$PB_var_gmax_s), ]

only_PB_stab <- readRDS(here::here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS")) %>%
  filter(
    num_strains == 9,
    waittime == 1e6,
    var_treat == "PB",
    Species == "SB_tot"
  )
only_PB_stab <- only_PB_stab[order(only_PB_stab$PB_var_gmax_s), ]

@@

stab_9s <- readRDS(here("data", "0_ss_finding", "temporal_method", "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))

@@

```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method", "processed_data", "stab_data_temporal_method.RDS"))
which_strains <- c(2, 3, 6, 9)
which_wait_time<- 1e6
figure_title <- " "

@@

## here the version with only one strain per group
all_stab <- readRDS(here("data", "0_ss_finding", "temporal_method",
                         "ele_rev1.1",
                         "stab_data_temporal_method_ELErevision1.1.RDS"))

@@

```{r echo = FALSE}
nine_strains <- readRDS(here("data",
                          "0_ss_finding",
                          "temporal_method",
                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
maxtolonly_strains <- readRDS(here("data",
                          "0_ss_finding",
                          "temporal_method",
                          "ele_rev1.1",
                          "ss_data_-1strains_waittime1e+06_event_definition_2.RDS"))

@@

all_stab_results_small <- readRDS(here("data/0_ss_finding/temporal_method/processed_data/stab_data_temporal_method.RDS"))

>>>>

```{r echo = FALSE}
rm(list = ls())
library(tidyverse)
library(microxanox)
library(patchwork)
library(here)
source(here("r", "various_useful_functions.r"))
# source(here("experiments", "1_figures_main_ms", "ms_figure_functions.r"))
source(here("R/ms_figure_functions.R"))

@@

```{r}
microxanox_version_here <- "0.9.1"
microxanox_version_path <- paste0("microxanox_v", microxanox_version_here)
if (packageVersion("microxanox") < package_version(microxanox_version_here)) {
  stop(paste0("microxanox version needs to be at least ", microxanox_version_here))
}
print(paste0("Version of microxanox: ", microxanox_version_here))
```

@@

```{r repl-meth1, echo=FALSE, eval = TRUE}
repl_meth <- readRDS(here("data",
                          microxanox_version_path,
                          "replication_method",
                          "event_definition_2",
                          "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
temp_meth <- readRDS(here("data",
                          microxanox_version_path,
                          "temporal_method",
                          "event_definition_2",
                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
```

@@

```{r both-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:both-meth1)', fig.height=8, fig.width=8, fig.align="center"}

repl_method_1 <- repl_meth$ss_res[[1]] %>%
     mutate(time = NA,
            direction = ifelse(initial_N_CB == 1, "up", "down")) %>%
  select(names(temp_meth$ssfind_result[[1]]))

@@

```{r div-repl-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-repl-meth1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data", 
                         microxanox_version_path,
                         "replication_method",
                         "event_definition_2",
                         "processed_data",
                         "all_stab_data.RDS"))

sim_length <- 1e6 ## currently a problem in how sim length is parsed by the data processing step
num_strains <- 9
plot_here <- all_stab %>%
  filter(simlength == sim_length)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

```{r repl-meth-ex1, echo = FALSE,  include=TRUE, fig.cap='(ref:repl-meth-ex1)', fig.height=10, fig.width=8, fig.align="center"}
repl_meth <- readRDS(here("data",
                          microxanox_version_path,
                          "replication_method",
                          "event_definition_2",
                          "ss_data_9strains_sim_length1e+06_event_definition_2.RDS"))
fig_state_vs_o2diff_sidebyside_alternative(repl_meth[94,])
```

@@

```{r div-temp-eventdef1, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-eventdef1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data",
                          microxanox_version_path,
                          "temporal_method",
                          "event_definition_1",
                          "processed_data",
                         "all_stab_data.RDS"))

sim_length <- 1e6
num_strains <- 9
plot_here <- all_stab %>%
  filter(waittime == wait_time)
p1 <- fig_div_vs_o2diff_1strain_7row(plot_here,
                                     which_strain = num_strains,
                                     figure_title = paste0(sim_length,
                                                           " simulation length,\n",
                                                           num_strains,
                                                           " strains"))
p2 <- fig_resilience_vs_div(plot_here,
                            which_strain = num_strains,
                            figure_title = " ")
p1 + p2

@@

```{r div-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-temp-meth1)', fig.height=7, fig.width=6, fig.align="center"}
all_stab <- readRDS(here("data",
                         microxanox_version_path,
                         "temporal_method",
                         "event_definition_2",
                         "processed_data",
                         "all_stab_data.RDS"))

@@

```{r ss-temp-meth3, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth3)', fig.height=10, fig.width=8, fig.align="center"}

## data made with the "run_single_sim.r" file in the ss_find, temporal method folder.

single_1e6 <- readRDS(here("data",
                           microxanox_version_path, 
                           "temporal_method",
                           "single_sims",
                           "single_1e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_1e6
fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
```

@@

```{r ss-temp-meth4, eval = FALSE, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth4)', fig.height=10, fig.width=8, fig.align="center"}
single_2e6 <- readRDS(here("data",
                           microxanox_version_path, 
                           "temporal_method",
                           "single_sims",
                           "single_2e6_result.RDS"))
temp_meth[1,]$ssfind_result[[1]] <- single_2e6
fig_state_vs_o2diff_sidebyside_alternative(temp_meth[1,])
```

@@

```{r ss-temp-meth1, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth1)', fig.height=10, fig.width=8, fig.align="center"}
wait_time <- "1e+04"
ss_9s <- readRDS(here::here("data",
                            microxanox_version_path, 
                            "temporal_method",
                            "event_definition_2",
                            paste0("ss_data_9strains_waittime", wait_time, "_event_definition_2.RDS")))
#stab_9s <- readRDS(here::here(\"data", "0_ss_finding", "temporal_method", microxanox_version_path, paste0("stab_data_9strains_waittime", wait_time, "_event_definition_2.RDS"))

@@

fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[14,])

@@

```{r ss-temp-meth2, echo = FALSE,  include=TRUE, fig.cap='(ref:ss-temp-meth2)', fig.height=10, fig.width=8, fig.align="center"}
fig_state_vs_o2diff_sidebyside_alternative(only_SB_variable[15,])
```

@@

```{r eval = run_sims_this_section, echo = FALSE}
var_expt_levels <- var_expt[,1:6]
no_diversity <- which(rowSums(abs(var_expt_levels))==0)
max_diversty_all <- which(max(rowSums(abs(var_expt_levels))) ==
                            rowSums(abs(var_expt_levels)))
max_only_CB_diversity <- which(max(rowSums(abs(var_expt_levels[,1:2]))) ==
                            rowSums(abs(var_expt_levels[,1:2])) &
                              rowSums(abs(var_expt_levels[,3:6]))==0)
max_only_SBPB_diversity <- which(max(rowSums(abs(var_expt_levels[,3:6]))) ==
                            rowSums(abs(var_expt_levels[,3:6])) &
                              rowSums(abs(var_expt_levels[,1:2]))==0)
```

@@

sim_res_novar1 <- run_simulation(parameter)

saveRDS(sim_res_novar1, here("data",
                             microxanox_version_path,
                             "temporal_method",
                             "puzzles",
                             "puzzle1_1.RDS"))
```

@@

```{r  sb-div-effect3, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect3)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_novar1 <- readRDS(here("data",
                             microxanox_version_path,
                             "temporal_method",
                             "puzzles",
                             "puzzle1_1.RDS"))
p <- plot_dynamics(sim_res_novar1)
p[[1]] <- p[[1]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[2]] <- p[[2]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[3]] <- p[[3]] + 
  xlab(NULL) + 
  ylab(expression(log[10](density)~(cells~L^{-1}))) +
  theme_bw()
p[[4]]$data <- p[[4]]$data %>% 
  dplyr::filter(species != "a")
p[[4]]$data$species <- p[[4]]$data$species %>%
  dplyr::recode(SO = "Oxidised sulfur", O = "Oxygen", SR = "Sulfide", P = "Phosphorus")
p[[4]] <- p[[4]] + 
  xlab("time (h)") + 
  ylab(expression(log[10](concentration)~(µM))) + 
  labs(colour = "substrate") +
  theme_bw()

@@

```{r  eval = run_sims_this_section, echo = FALSE}
parameter$strain_parameter <- var_expt[max_only_SBPB_diversity,]$pars[[1]]
#parameter$sim_duration <- 100000
#parameter$result <- NULL
#parameter$log10a_series <- c(-5.2, -5.2)
#parameter$strain_parameter$initial_state <- new_initial_state(
#  nrow(parameter$strain_parameter$CB),
#  nrow(parameter$strain_parameter$PB),
#  nrow(parameter$strain_parameter$PB),
#  values = "bush_ssfig3"
#)
parameter$strain_parameter$initial_state[grep("CB_", names(parameter$strain_parameter$initial_state))] <- 10^10/nrow(parameter$strain_parameter$CB)
sim_res_highvar1 <- run_simulation(parameter)
saveRDS(sim_res_highvar1,
        here("data",
             microxanox_version_path,
             "temporal_method",
             "puzzles",
             "puzzle1_2.RDS"))
```

@@

```{r sb-div-effect4, echo = FALSE,  include=TRUE, fig.cap='(ref:sb-div-effect4)', fig.height=8, fig.width=8, fig.align="center"}
sim_res_highvar1 <- readRDS(here("data",
             microxanox_version_path,
             "temporal_method",
             "puzzles",
             "puzzle1_2.RDS"))

@@

```{r echo = FALSE}
ss_9s <- readRDS(here("data",
                            microxanox_version_path,
                            "temporal_method",
                            "event_definition_2",
                            "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
only_PB_variable <- ss_9s %>%
  filter(
    abs(CB_var_gmax_s) < 0.0001,
    abs(SB_var_gmax_s) < 0.0001
  )
only_PB_variable <- only_PB_variable[order(only_PB_variable$PB_var_gmax_s), ]

only_PB_stab <- readRDS(here("data",
                                   microxanox_version_path,
                                   "temporal_method",
                                   "event_definition_2",
                                   "processed_data",
                                   "all_stab_data.RDS")) %>%
  filter(
    num_strains == 9,
    waittime == 1e6,
    var_treat == "PB",
    Species == "SB_tot"
  )
only_PB_stab <- only_PB_stab[order(only_PB_stab$PB_var_gmax_s), ]

@@

stab_9s <- readRDS(here("data", 
                        microxanox_version_path,
                        "temporal_method", 
                        "event_definition_2",
                        "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))

@@

```{r div-stab-multstrain1, echo = FALSE,  include=TRUE, fig.cap='(ref:div-stab-multstrain1)', fig.height=8, fig.width=8, fig.align="center"}
all_stab <- readRDS(here("data",
                         microxanox_version_path,
                         "temporal_method", 
                         "event_definition_2",
                         "processed_data", "all_stab_data.RDS"))
which_strains <- c(2, 3, 6, 9)
which_wait_time<- 1e6
figure_title <- " "

@@

## read the data
all_stab <- readRDS(here("data",
                         microxanox_version_path,
                         "temporal_method", 
                         "event_definition_2",
                         "processed_data",
                         "all_stab_data.RDS"))

@@

```{r echo = FALSE}
nine_strains <- readRDS(here("data",
                         microxanox_version_path,
                         "temporal_method", 
                         "event_definition_2",
                          "ss_data_9strains_waittime1e+06_event_definition_2.RDS"))
maxtolonly_strains <- readRDS(here("data",
                         microxanox_version_path,
                         "temporal_method", 
                         "event_definition_2",
                          "ss_data_-1strains_waittime1e+06_event_definition_2.RDS"))

@@

all_stab_results_small <- readRDS(here("data",
                         microxanox_version_path,
                         "temporal_method", 
                         "event_definition_2",
                         "processed_data", "all_stab_data.RDS"))
